
\section{Discussion}
\label{sec:discuss}

Bleu is a precision metric. 
Consider the following candidate/reference pair:
\begin{center}
  the the the the the the the \\
the cat on the mat
\end{center}

We call this the  the overgeneration problem (the two the tokens are not a typo)
We handle this problem by removing a the in the reference each time it is matched . 
This takes care of the the overgeneration problem in the standard BLEU metric. 
The the overgeneration problem remains in our method. 
Consider the candidate reference pair:
\begin{description}
\item[System Output] 
\end{description}
The price for the weapon I learned there
I found out the price of the weapon only there
The word ``for'' does not appear in the reference. 
Our method obtains similarity scores between ``for'' and each word in the reference that has not been matched yet. 
Unfortunately, the word with highest similarity to ``for'' is ``there. 
``there" is chosen as the match for ``for'' and is removed from the referenced word list. 
When we later try to find a match for ``there'' an exact match is not made. 
In this case the standard BLEU metric assigns a higher score to the candidate than our method. 

The xleu metric assigns a perfect match to the pair of $4$-grams in table~\ref{tab:perfect}. 
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
    candidate & reference & similarity \\
the woman drove around & woman drove around the & 1.0 
  \end{tabular}
  \caption{XLEU assigns a perfect match to this pair of $4$-grams.}
  \label{tab:perfect}
\end{table}

This is a problem. 
The metric is assigning perfect scores to $n$-grams that are  badly ordered. 
If the system and reference have the same words in different orders a perfect score is assigned to the $n$-gram.
This happens because the vector representation of the $4$-gram is taken as the average of each of its component $1$-grams. 

The pair in table~\ref{tab:good} is an example of a good score assignment by XLEU. 

\begin{table}[hh]
  \centering
  \begin{tabular}{|c|c|c||c|c|c|}
    drove around the store & went around the store & 0.93 
  \end{tabular}
  \caption{A good score assignment by XLEU.}
  \label{tab:good}
\end{table}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ling848fall2014"
%%% End: 
